---
title: "lab 2"
author: "Yunwei Zhang"
date: "April 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Juul's IGF data
Description
The juul data frame has 1339 rows and 6 columns. It contains a reference sample
of the distribution of insulin-like growth factor (IGF-1), one observation per
subject in various ages with the bulk of the data collected in connection with
school physical examinations.
Format
This data frame contains the following columns:
age: a numeric vector (years).
menarche: a numeric vector. Has menarche occurred (code 1: no, 2: yes)?
sex: a numeric vector (1: boy, 2: girl).
igf1: a numeric vector. Insulin-like growth factor.
tanner: a numeric vector. Codes 1-5: Stages of puberty a.m. Tanner.
testvol: a numeric vector. Testicular volume (ml). 

```{r}
#install.packages("ISwR")
library("ISwR")

data(juul)

#do not want to entire data
juul1 <- subset(juul,age > 8 & age < 20 & complete.cases(menarche))
summary(juul1)


```


```{r}
#factor needed
juul1$menarche <- factor(juul1$menarche,labels=c("No","Yes"))
juul1$tanner <- factor(juul1$tanner)
attach(juul1)

#perform logistic regression
summary(glm(menarche ~ age,binomial))


```

```{r}
summary(glm(menarche ~ age+tanner,binomial))


```


Log odds ratio for one year increase in age is









0.8603
Odds ratio is 








exp(0.8603) = 2.364
Log odds ratio for a two year increase in age is 










(2)(0.8603) = 1.7206
Odds ratio is 









exp(1.7206) = 5.588
All these holding tanner score constant
Log odds ratio for tanner 4 vs. tanner 1 is 








2.5645
Odds ratio is 













exp(2.5645) = 12.994
Log odds ratio for tanner 4 vs. tanner 3 is 











2.5645 - 0.8264 = 1.7381
Odds ratio is 















exp(1.7381) = 5.687
All these holding age constant


Can you get the confidence interval for the parameters?
Can you get the predicted value?



```{r}
write.table(juul,file="juul.txt")

confint.default(glm(menarche ~ age+tanner,binomial))
#predict(glm(menarche ~ age+tanner,binomial),type = "response")
```

Evans County, GA Dataset (1963)
??? Data are in evans.dat (text, no header), evans.sas7bdat
(SAS version 9 dataset), evans.sav (SPSS dataset), and
evans.dta (Stata dataset) on the website given in the
syllabus.
??? The data are from a cohort study in which 609 white
males were followed for 7 years, with coronary heart
disease as the outcome of interest.

read.table, read.csv, etc. are all variants that
can handle text file input with different
defaults.
By default, reads strings as factors, unless
stringsAsFactors=F. Often this option is a good
idea.

Variable Description
ID Subject ID, one observation per subject
CHD Coronary heart disease (1) or not (0)
CAT High catecholamine level (1) or not (0)
AGE Age in years
CHL Cholesterol level (mg/dL)
SMK Ever smoked (1) or never smoked (0)
ECG ECG abnormality (1) or not (0)
DBP Diastolic blood pressure (mm)
SBP Systolic blood pressure (mm)
HPT = 1 if DBP ???90 or SBP ??? 160, otherwise = 0
CH CAT*HPT
CC CAT*CHL
```{r}
vars <- c("ID","CHD","CAT","AGE","CHL","SMK","ECG","DBP","SBP","HPT","CH","CC")
evans <- read.table("D:\\school in california\\Aucdavis\\TA\\hw3\\lesson data.txt",header=F,col.names=vars)
summary(evans)
 plot(SBP ~ AGE, data=evans) #Systolic Blood Pressure vs. Age
abline(coef(lm(SBP~AGE,data=evans)),lwd=2) #Puts regression line on the plot
abline(h=140,col="blue",lwd=2) #line at current hypertension threshold
abline(h=160,col="red",lwd=2) #line at hypertension threshold used in study
title("Systolic Blood Pressure by Age")
```


```{r}
model1=glm(CHD~CAT+AGE+CHL+SMK+HPT,family=binomial,data=evans)
summary(model1)


```

```{r}



```









```{r}
anova(glm(menarche ~ age+tanner,binomial),test="Chisq")

```





Question:how to choose the predictors to be included to get the best regression?
i.e. whether to include the square or not whether to include interaction term or not?



```{r}
 drop1(glm(menarche ~ age+tanner,binomial),test="Chisq")

```


??? The deviance under the normal distribution is just the residual sum of squares.
??? Changes in normal deviance is usually assessed by the F- test in an ANOVA table.
??? For logistic regression, differences in deviance are assessed using the chi-squared distribution with degrees of freedom equal to the number of parameters omitted between the
larger and smaller model.
??? The latter test is approximate (asymptotic).
??? Tests of coefficients are based on the Wald test in which we have an estimate and an estimated variance. This too is approximate and not identical to the likelihood ratio
(deviance) test.

```{r}
deviance(glm(hyp.tbl ~ smoking+obesity+snoring,family=binomial))

deviance(glm(hyp.tbl ~ smoking*obesity*snoring,family=binomial))

deviance(glm(hyp.tbl ~ 1,family=binomial))

logLik(glm(hyp.tbl ~ smoking+obesity+snoring,family=binomial))

logLik(glm(hyp.tbl ~ smoking*obesity*snoring,family=binomial))

```





















