---
title: "lab3 20180412"
author: "Yunwei Zhang"
date: "April 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note : I am using Rmarkdown here since you can write English , write Latex, make title, etc easily between what we called "chuck" (where you write your code).

##evans data and model selection

###Today we will focus mostly on how to do model selection on the evans data.
Belows are the discription of the evans data.

Evans County, GA Dataset (1963)
??? Data are in evans.dat (text, no header), evans.sas7bdat
(SAS version 9 dataset), evans.sav (SPSS dataset), and
evans.dta (Stata dataset) on the website given in the
syllabus.
??? The data are from a cohort study in which 609 white
males were followed for 7 years, with coronary heart
disease as the outcome of interest.


Variable Description

ID Subject ID, one observation per subject
CHD Coronary heart disease (1) or not (0)
CAT High catecholamine level (1) or not (0)
AGE Age in years
CHL Cholesterol level (mg/dL)
SMK Ever smoked (1) or never smoked (0)
ECG ECG abnormality (1) or not (0)
DBP Diastolic blood pressure (mm)
SBP Systolic blood pressure (mm)
HPT = 1 if DBP 90 or SBP 160, otherwise = 0
CH CAT*HPT
CC CAT*CHL

```{r}
#since the txt file does not have the column names, we add the columns of our predictors and dependent variable by hand
vars <- c("ID","CHD","CAT","AGE","CHL","SMK","ECG","DBP","SBP","HPT","CH","CC")
#load the data, notice that "header=False"
evans <- read.table("D:\\school in california\\Aucdavis\\TA\\hw3\\lesson data.txt",header=F,col.names=vars)
#preview of the data
summary(evans)

```

```{r}
#fit the full model
#I will let you figure out which predictors should be factored, belows are just code examples.
model1=glm(CHD~CAT+AGE+CHL+SMK+HPT,family=binomial,data=evans)
#get the summary
summary(model1)


```

```{r}
#for the reduced model ,you can do whatever you want.
#I use the one has the intersection term as an example.
model2<-glm(CHD~CAT+AGE+CAT*AGE,family=binomial,data=evans)
summary(model2)


```


#There are the summary of the commands you can use to judge your model based on what knid of criteria you want to use.

```{r}
#get all the deviance from the glm model
anova(model1)
anova(model2)
#get the AIC
AIC(model1)
#get the deviance
deviance(model1)
#get the loglikelihood
logLik(model1)

```

#backward elimination method for model selection

```{r}
#drop one term at a time
drop1(model1,test="Chisq")


```

















