---
title: "lab4"
author: "Yunwei Zhang"
date: "April 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Confidence interval topic

First of all, we will take a look at the evans data:
```{r}
vars <- c("ID","CHD","CAT","AGE","CHL","SMK","ECG","DBP","SBP","HPT","CH","CC")
evans <- read.table("D:\\school in california\\Aucdavis\\TA\\hw3\\lesson data.txt",header=F,col.names=vars)
summary(evans)


```

Build a model and check the coefficient of it.
```{r}
model1=glm(CHD~CAT+CHL+SMK+HPT+CAT*CHL+CAT*HPT,binomial,data=evans)
summary(model1)
coef(model1)
```

##Notice that:
Confidence intervals and tests for single coefficients
are given in the summary(glm()) output or are easily
derived.

## some preparation for calculating C.I.(confidence interval) for interaction terms or categorical data has multi-levels or also different contrast.
Interaction Terms
??? An interaction means that the effect of one variable
depends on the level of another.
??? To get a numerical measure of effect such as odds ratio,
we need to specify the level of the other one.
??? We can set the other variable at the modal level, the
median level, or the mean level, or at a variety of levels


Contrasts
??? A contrast is a weighted combination of factor levels in
which the weights add up to 1.
??? We can change the coding of a factor with five levels
from an intercept and four 0/1 variables to a set of
contrasts.
??? This can be complex and hard to implement.
??? There are other R packages that can handle these
separately such as multcomp. But personally, I do not recommand you to use that.


We need the quantile
```{r}
t=qnorm(0.975)
t
#qchisq()
```


We need to do more work to find confidence intervals
and tests for differences of coefficients as when a factor
has more than two levels.
The same trick allows us to get confidence intervals
and tests for interaction terms.

```{r}
model2<-glm(CHD~CAT+CHL+HPT+CAT*HPT,binomial,evans)
c1 <- coef(model2)
v1 <- vcov(model2)
c1
v1
```

```{r}
#calculate the "new mean"
b1 <- c(0,1,0,0,1) 
t(b1) %*% c1


```

Effect of CAT when HPT = 1 is 2.191 - 1.681 = 0.5093 

```{r}
 v <- vcov(model2)
v
#calculate the "new variance"
t(b1) %*% v %*% b1
```

```{r}
#take the square root
sqrt(t(b1) %*% v %*% b1)

```
Log odds ratio CI is 0.5093 ± (1.960)(0.3529) 



##some introduction of the Byssinosis data for doing hw2

```{r}
dt1<-read.csv("D:\\school in california\\Aucdavis\\TA\\hw2\\Byssinosis.csv")
dt1$Smoking=factor(dt1$Smoking)
dt1$Sex=factor(dt1$Sex)
dt1$Race=factor(dt1$Race)
dt1$Workspace=factor(dt1$Workspace)
dt1$Employment=factor(dt1$Employment)
dt1$y=cbind(dt1$Byssinosis,dt1$Non.Byssinosis)
model1<-glm(dt1$y~Smoking+Sex+Race+Employment+Workspace,data=dt1,binomial)
summary(model1)
anova(model1)



```

Interaction Terms
??? An interaction means that the effect of one variable
depends on the level of another.
??? To get a numerical measure of effect such as odds ratio,
we need to specify the level of the other one.
??? We can set the other variable at the modal level, the
median level, or the mean level, or at a variety of levels

##Alternative:using the evans data before
We can re-run the analysis with a different default level for the categorical variable so that the desired comparison is a single
coefficient.

relevel {stats} Reorder Levels of Factor
The levels of a factor are re-ordered so that the
level specified by ref is first and the others are
moved down.
relevel(x, ref, ...)
x an unordered factor.
ref the reference level, typically a string.

Variable Description

ID Subject ID, one observation per subject
CHD Coronary heart disease (1) or not (0)
CAT High catecholamine level (1) or not (0)
AGE Age in years
CHL Cholesterol level (mg/dL)
SMK Ever smoked (1) or never smoked (0)
ECG ECG abnormality (1) or not (0)
DBP Diastolic blood pressure (mm)
SBP Systolic blood pressure (mm)
HPT = 1 if DBP ???90 or SBP ??? 160, otherwise = 0
CH CAT*HPT
CC CAT*CHL
```{r}
?relevel

evans$SMK<-relevel(evans$SMK,ref=0)
evans$SMK
#make the data more readable: let 0 becomes no and 1 becomes yes for example.
evans$SMK[evans$SMK==0]="no"
evans$SMK
evans$SMK[evans$SMK==1]="yes"
evans$SMK=factor(evans$SMK)
evans$SMK<-relevel(evans$SMK,ref="yes")
```












