---
title: "lab5"
author: "Yunwei Zhang"
date: "April 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##important feedback on hw

#hw1
For students: you need to be careful if you use odds ratio inference group/A(our normal/diabetic in the question) in your interpretation, since in the output, what you directly get is A/inference group.

#hw2
1.Same problem for question 2 part 1 as in hw1.
2.For question 2 the last part, some students get the wrong deviance, you need to be careful.

##topic:model selection

```{r}
#add1() drop1() methods

#using evans data
vars <- c("ID","CHD","CAT","AGE","CHL","SMK","ECG","DBP","SBP","HPT","CH","CC")
#load the data, notice that "header=False"
evans <- read.table("D:\\school in california\\Aucdavis\\TA\\hw3\\lesson data.txt",header=F,col.names=vars)

```

drop1 starts from the full model
drop1(object, scope, test = c("none", "Rao", "LRT",
"Chisq", "F"),k = 2, ...)

object :your glm model
scope is the set of things that can be dropped. Usually,
this is omitted, meaning that any term in the model can be
dropped, though hierarchy of interactions is respected
automatically.

test is for logistic regression usually "Chisq" or "LRT",
both of which produce the likelihood ratio test.

```{r}
model1<-glm(CHD ~ CAT+CHL+SMK+HPT,family=binomial,data=evans)
 drop1(model1,test="Chisq")
```


As for add1 you can specify the "scope" to define the range where r can choose to add for your existing model.


```{r}
add1(model1,scope=~CAT*CHL*SMK*HPT,test="Chisq")
```

Best AIC from adding CAT:CHL, next best from adding CAT:HPT.
HPT not significant, but AIC and significant interaction don't suggest
dropping. 

##stepwise method


Backward stepwise only drops terms.
Forward stepwise only adds terms.
Default is "both" which can either add or drop,
whichever provides the most improvement.

```{r}
step(model1,scope=~CAT*CHL*SMK*HPT)
```























